Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection

### 2019-06-17 reports/paper1/paper.tex
Revise paper

\documentclass{proc}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[round]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements

@@

\title{Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection}
\date{2019}
\author{
  Sherman Lo \and Jason Warnett \and Gregory Gibbons \and Mark Williams \and Thomas Nichols \and Julia Brettschneider 
}

@@

\maketitle

\begin{abstract}
X-ray computed tomography can be used for defect detection in additive manufacturing (AM). Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features. To avoid this time-consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection. An AM sample was manufactured with voids to see if they can be detected. The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test. The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved. Voids with diameters in the order of millimetres were detectable.
\end{abstract}

@@

Additive manufacturing (AM) is capable of manufacturing objects with complicated internal and external geometries \citep{wong2012review, ngo2018additive}. One example of AM technology is fused deposition modelling (FDM) \citep{crump1991fused, crump1992apparatus, stratasys2019what}. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in a form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer. The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer.

However, there is a need for product inspection and in particular assessing the quality of the internal structures. For example, voids can form between layers which can hinder the mechanical properties of the product \citep{wang20173d, ngo2018additive}. In power based AM technologies, gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}. Low wetting ability of the melt pool can cause balling, this is where the sintered powder has poor contact on the existing layer causing spherical particles to form on the surface of the AM part \citep{li2012balling, gu2009balling}.

Non-destructive testing can be used to assess the quality of the product such as x-ray computed tomography (XCT) \citep{kruth2011computed, sun2012overview}. The object is held by foam on a turntable and placed between an x-ray source and an x-ray detector. X-ray projections are taken while the object rotates. Typically the x-ray is a cone beam. The x-ray projections are then used to reconstruct the object in 3D \citep{brooks1976principles, feldkamp1984practical, smith1990cone}.

In AM, XCT is commonly used for the investigation of pores \citep{thompson2016x}. Pores can be classified as defects if the pores are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}. The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}. However more accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.

The strength of XCT comes from the fact that the location of the pores can be visualised. Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}. \cite{leuders2015fatigue} pointed out that the location of the pores is an important factor. In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.

The disadvantage of x-ray CT is that it involves the acquisition and reconstruction of thousands of projections of the sample. Even in the marketing of \cite{nikon2015inline}'s inline quality control featured automatic reconstruction in the background with a progress bar. The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards} however more images would improve the accuracy of the reconstruction \citep{kruth2011computed}.

Instead of reconstructing the object, the analysis can be done on a single x-ray projection itself by comparing it to a simulated projection such as \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \cite{brierley2018optimized} demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without. It is however inevitable that accuracy is lost from the jump from 3D to 2D \citep{hayden2009chest}.

It was investigated whenever defects can be detected from a single x-ray projection. This was done by obtaining an x-ray projection of an AM sample, with purposely designed voids, and comparing it with the simulation. The apparatus and procedures are shown in the methods section. In addition, software development and simulation studies were discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

An ABS plastic cuboid (\SI{40}{\milli\metre} $\times$ \SI{40}{\milli\metre} $\times$ \SI{60}{\milli\metre}) with voids was purposefully manufactured to see if they can be detected. The CAD shown in Figure \ref{fig:inference_testObject} was manufactured using a \emph{Fortus 400mc (Stratasys, US)} 3D printer. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise, they were arranged irregularly. The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$.

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
  \caption{The CAD of a cuboid with voids. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise, they were arranged irregularly. The scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}. The \SI{225}{\kilo\volt} source was used with a $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}. The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}. A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects were negligible. 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}. A shading correction \citep{young2000shading, munzenmayer2003enhancing} was applied to each projection using a black (\SI{0}{\kilo\volt}) and white image (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.

The projection of the sample was obtained and repeated 20 times at a fixed angle. The 20 projections were split into 2. 19 random projections were held out. The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \emph{aRTist} can simulate projections of the sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the
CAD of the sample \citep{bellon2011simulation, deresch2012simulating}. \emph{aRTist} was used to obtain a simulation projection as if the voids were not there. Numerical methods were used to align the simulated projection to the obtained projection. A shading correction was applied to the simulated projection using a flat black image and a simulated white image.

@@

A method was proposed to compare a single projection with a simulation of that projection and treating it as the ground truth. This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test. A disagreement too big will classify that pixel as a positive result. Beforehand, however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.

@@

The variance model, $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}. The fitting of the model was done using the held out replicated projections of the sample. These replicated projections were manually segmented. This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model. The model used was a gamma distributed generalised linear model \citep{nelder1972generalized, mccullagh1984generalized} with an identity link. The variance was predicted using the grey value in the simulated projection as the predictor variable when working out the test statistics.

@@

To obtain the estimates, a circular kernel with radius $r$ was centred at $(x,y)$. All the pixels captured by the circular kernel and the region of interest (ROI) were pooled together to obtain a kernel density estimate \citep{parzen1962on, friedman2001elements}
\begin{equation}
\widehat{p}_{Z_{x,y}}(z) = 
\frac{1}{nh}
  \sum_{i,j\in K_{x,y}}\phi\left(
    \dfrac{z_{i,j}-z}{h}
  \right)
\end{equation}
where $K_{x,y} = \text{kernel centred at }(x,y) \cap \text{ROI}$, $n$ is the number of pixels captured by $K_{x,y}$, $\phi(z)$ is the probability density function of a standard Normal random variable and $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_{x,y},\text{IQR}_{x,y}/1.34\right)
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of the test statistics in $K_{x,y}$, similar to \cite{silverman1986density, sheather2004density}. The estimates were obtained by solving
\begin{equation}
\widehat\mu_{0,x,y} = \text{argmax} \widehat{p}_{Z_{x,y}}(z)
\end{equation}
using the Newton-Raphson method and
\begin{equation}
  \widehat{\sigma}_{0,x,y} = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z=\widehat{\mu}_{0,x,y}}
  \right]^{-1/2}
\end{equation}
\citep{efron2004large}. The test statistics were normalised using
\begin{equation}
  T_{x,y} = 
  \dfrac{
    Z_{x,y}-\widehat{\mu}_{0,x,y}
  }
  {
    \widehat{\sigma}_{0,x,y}
  } \ .
\end{equation}
All the normalised test statistics were converted to $p$-values
\begin{equation}
  p_{x,y} = 2(1-\Phi(|t_{x,y}|))
\end{equation}
and was used in the \cite{benjamini1995controlling} (BH) procedure at the 5\% FDR level to classify pixels as positive or not for defects.

\subsection{Software Development}

The empirical null filter was implemented using \emph{ImageJ} \citep{abramoff2004image, schindelin2012fiji, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}. It contains implementations of filters, such as the mean filter and median filter, using a circular kernel and multiple threads. Each thread filters a row in parallel.

@@

Contamination is the result of a linear transform of the test statistics $Z_{x,y}$. For example in this experiment, the image was multiplied by 2 and a gradient was added to it. Suppose the image does contain defects, then an example of a resulting distribution is
\begin{align}
  Z_{x,y}|H_{0,x,y}&\sim\normal(\mu_{0,x,y},2^2)
  \\
  Z_{x,y}|H_{1,x,y}&\sim\normal(2\mu_1+\mu_{0,x,y},2^2)
\end{align}
where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. This was used in this study to simulate a contaminated image with defects. The contaminated square defected image is shown in Figure \ref{fig:inference_defectSquare2Example}.

@@

Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null. In this simulated example, it is about $r>\SI{54}{\pixel}$. A kernel too small would treat the defects as null, making them difficult to detect.

The receiver operating characteristic (ROC) curve \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use} was studied in this experiment. The ROC is a parametric plot, plotting the true positive rate (sensitivity) against the false positive rate ($1-\text{specificity}$) for varying thresholds. The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}. Interpretations of the area do exist \citep{metz1978basic,hanley1982meaning} and discussed thoroughly in \cite{cook2007use}.

@@

\begin{figure*}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
        \caption{ROC area}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{ROC area and various errors obtained when conducting a hypothesis test on a $\SI{256}{\pixel} \times \SI{256}{\pixel}$ filtered contaminated Gaussian image with a $\SI{30}{\pixel}\times \SI{30}{\pixel}$ square defect. Various kernel radiuses were investigated. The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image with a defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. The test was done at the 5\% FDR level. The box plot summarise the 100 repeated measurements of the experiment.}
  \label{fig:inference_Experiment_DefectRadiusSquare}
\end{figure*}

@@

The result from the simulation is shown Figure \ref{fig:inference_Experiment_DefectRadiusSquare}. The ROC area increased with kernel radius which highlighted that a filtered image with a good radius kernel can performance almost as well as though there was no contamination. It also appeared that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.

@@

In the experiment with the AM sample, the x-ray projection was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the sample. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. The resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{X-ray projection with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{\pixel}$. a) X-ray projection with highlighted red positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure*}

@@

The main issue was how slow the filter was. Figure \ref{fig:inference_timing} shows the timings of the empirical null filter and the mean variance filter. For a filter to take more than a minute is unacceptable when used on the production line when typical filters can take a fraction of a second.

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean variance null filter}
      \end{subfigure}
    }
  \caption{Timings when filtering a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ image. The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image. Note that the $y$-axis changes scale. The box plot summarise the 100 repeated measurements of the timings.}
  \label{fig:inference_timing}
\end{figure*}

>>>>

\documentclass{article}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[square,semicolon]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements
\usepackage[figurename=Fig.]{caption}
\usepackage[numbib]{tocbibind} %number references and figure title
\usepackage{authblk}

@@

%to number list of figures
\renewcommand{\listoffigures}{\begingroup
\tocsection
\tocfile{\listfigurename}{lof}
\endgroup}

\title{Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection}
\author[1, *]{S.E.~Lo}
\author[2]{J.W.~Warnett}
\author[2]{G.J.~Gibbons}
\author[2]{M.A.~Williams}
\author[3]{T.E.~Nichols}
\author[1]{J.A.~Brettschneider}
\affil[1]{Department of Statistics, University of Warwick, Coventry, CV4 7AL, UK}
\affil[2]{Warwick Manufacturing Group, University of Warwick, Coventry, CV4 7AL, UK}
\affil[3]{Big Data Institute, Old Road Campus, University of Oxford, Oxford, OX3 7LF, UK}
\affil[*]{Corresponding author: s.ip@warwick.ac.uk, +442476574812}

@@

\begin{titlepage}
\maketitle

\begin{abstract}
\noindent
\textbf{BACKGROUND}: X-ray computed tomography can be used for defect detection in additive manufacturing (AM). Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features.
\newline
\textbf{OBJECTIVE}: It was investigated whenever it is possible to detect defects based on a single angular projection. The motivation behind it is that defect detection in projection space should be faster than in reconstruction space.
\newline
\textbf{METHODS}: An AM sample was manufactured with voids to see if they can be detected. The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test. The simulation was not perfect which led to misleading results. The empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
\newline
\textbf{RESULTS}: Voids with diameters in the order of millimetres were detectable. Simulation studies have shown that statistical properties such as the false discovery rate were preserved when using the filter.
\newline
\textbf{CONCLUSIONS}: Defect detection in projection space is possible. This can be extended to multiple independent projections in real time on a conveyor belt. The main bottle neck is the multiple evaluation of functions required for robust estimation in the empirical null filter. Speed up could be possible by implementing the filter on a GPU or exploring further robust estimators.
\newline
\newline
\emph{Keywords:} Hypothesis testing, local normalisation, image filtering, projection space, additive manufacturing, voids, defects, quality control
\end{abstract}

\end{titlepage}

@@

Additive manufacturing (AM) is an emerging technology that overcomes many traditional methods such as computer numerical control (CNC). In AM, the product is manufactured layer by layer to product complicated internal and external geometries \citep{ngo2018additive, wong2012review}. One common example of AM technology is fused deposition modelling (FDM) \citep{crump1991fused, crump1992apparatus, stratasys2019what}. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in a form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer. The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer. Powder based AM such as selective laser sintering \citep{3d2019our, deckard1989method, dtm1990the} can manufacture metal products.

There is a need for product inspection, in particular quality assessment of the internal structures. The properties of materials produced by AM are not yet fully understood. For example, voids can form between layers which can impact the mechanical properties of the product \citep{ngo2018additive, wang20173d}. In power based AM technologies, gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{tammas2015xct, thijs2010study}. Low wetting ability of the melt pool can cause balling, a phenomenon where spherical or ellipsoidal deposits on the surface of the AM part. They are formed by sintered powder with insufficient contact on the existing layer \citep{gu2009balling, li2012balling}.

Non-destructive testing, such as x-ray computed tomography (XCT), can be used to assess the quality of the product \citep{kruth2011computed, sun2012overview}. The object is held by foam on a turntable and placed between an x-ray source and an x-ray detector. X-ray projections are taken at a series of angles. Typically the x-ray is a cone beam. The x-ray projections are then used to reconstruct the object in 3D \citep{brooks1976principles, feldkamp1984practical, smith1990cone}.

In AM, XCT is commonly used for the investigation of pores \citep{thompson2016x}. Pores can be classified as defects if the pores are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{amrhein2014characterization, gandossi2010probability}. The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}. More accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.

An advantage of XCT is that the location of the pores can be visualised. Studies have shown a link between porosity and stress concentration \citep{carlton2016damage, leuders2015fatigue, siddique2015computed}. The location of the pores is a good predictor of fatigue strength \citep{leuders2015fatigue}. In addition to pores, surface deviation can be measured by aligning the reconstruction with the computer-aided design (CAD) model and measuring any discrepancies \citep{kim2016inspection, lee2015compliance, villarraga2015assessing}.

A disadvantage of XCT is that it involves the acquisition and reconstruction of thousands of projections of the sample. XCT is not a instantaneous process so progress bars are usually featured in marketing for XCT such as \emph{Nikon}'s inline quality control \citep{nikon2015inline}. Projection acquisition can take between 15 minutes to a number of hours \citep{warnett2016towards} but more projections would improve the accuracy of the reconstruction \citep{kruth2011computed}.

Instead of reconstructing the object, the analysis can be done on a single x-ray projection itself by comparing it to a simulated projection. It was demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without \citep{brierley2018optimized}. The simulated projections are made in software called \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}. It is however inevitable that information is lost from the jump from reconstruction space to projection space, for example a CT scan has superior performance in the diagnostic of pneumonia compared to a chest radiograph \citep{hayden2009chest}.

This paper investigates whether defects can be detected from a single x-ray projection. To validate our method, we designed an AM test cuboid with purposely designed voids. An x-ray projection was obtained and compared with the simulation from \emph{aRTist} in order to detect these voids. The simulation was not perfect which led to misleading results. The empirical null filter was used to cater for the model misspecification so that sensible inference was achieved. The apparatus and procedures are shown in the methods section. In addition, computational implementation and simulation studies of the empirical null filter are discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

An ABS plastic test cuboid (\SI{40}{\milli\metre} $\times$ \SI{40}{\milli\metre} $\times$ \SI{60}{\milli\metre}) with voids was purposefully manufactured to see if they can be detected. The CAD model of the test cuboid is shown in Fig.~\ref{fig:inference_testObject}. It was manufactured using a \emph{Fortus 400mc (Stratasys, US)} 3D printer. Six voids of each diameter, \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}, were designed in the CAD model. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly. The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$ \citep{hanseen2013fortus}.

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}. The \SI{225}{\kilo\volt} source was used with a $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}. The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}. A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects \citep{kueh2016modelling} were negligible. 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}. A shading correction \citep{munzenmayer2003enhancing, young2000shading} was applied to each projection using a black (\SI{0}{\kilo\volt}) and white image (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.

The projection of the sample was obtained and repeated 20 times at a fixed angle. 19 randomly selected projections were held out. The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}. \emph{aRTist} can simulate projections of the sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the
CAD of the sample \citep{bellon2011simulation, deresch2012simulating}. \emph{aRTist} was used to obtain a simulation projection as if the voids were not there. Numerical methods were used to align the simulated projection to the obtained projection. The same shading correction was applied to the simulated projection, but instead using a flat black image and a simulated white image.

@@

A method was proposed to compare a single projection with a simulation of that projection and treating it as the ground truth. This was done by using two-tailed multiple hypothesis testing \citep{fisher1970statistical, neyman1933on, pearson1900on} controlling the false discovery rate (FDR) \citep{benjamini2010discovering, benjamini1995controlling}, treating each pixel as an individual test. A disagreement too big will classify that pixel as a positive result. Beforehand, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.

@@

The variance model, $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}. The fitting of the model was done using the held out replicated projections of the sample. These replicated projections were manually segmented. This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model. The model used was a gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} with an identity link. The variance was predicted using the grey value in the simulated projection as the predictor variable when working out the test statistics.

@@

To obtain the estimates, a circular kernel with radius $r$ was centred at $(x,y)$. All the pixels captured by the circular kernel and the region of interest (ROI) were pooled together to obtain a kernel density estimate \citep{friedman2001elements, parzen1962on}
\begin{equation}
\widehat{p}_{Z_{x,y}}(z) = 
\frac{1}{nh}
  \sum_{i,j\in K_{x,y}}\phi\left(
    \dfrac{z_{i,j}-z}{h}
  \right)
\end{equation}
where $K_{x,y} = \text{kernel centred at }(x,y) \cap \text{ROI}$, $n$ is the number of pixels captured by $K_{x,y}$, $\phi(z)$ is the probability density function of a standard Normal random variable and $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_{x,y},\text{IQR}_{x,y}/1.34\right)
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of the test statistics in $K_{x,y}$, similar to Silverman's rule of thumb \citep{sheather2004density, silverman1986density}. The estimates were obtained by solving
\begin{equation}
\widehat\mu_{0,x,y} = \text{argmax} \widehat{p}_{Z_{x,y}}(z)
\end{equation}
using the Newton-Raphson method and
\begin{equation}
  \widehat{\sigma}_{0,x,y} = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z=\widehat{\mu}_{0,x,y}}
  \right]^{-1/2}
\end{equation}
\citep{efron2004large}. The test statistics were normalised using
\begin{equation}
  T_{x,y} = 
  \dfrac{
    Z_{x,y}-\widehat{\mu}_{0,x,y}
  }
  {
    \widehat{\sigma}_{0,x,y}
  } \ .
\end{equation}
All the normalised test statistics were converted to $p$-values
\begin{equation}
  p_{x,y} = 2(1-\Phi(|t_{x,y}|))
\end{equation}
and was used in the  Benjamini-Hochberg \citep{benjamini1995controlling}(BH) procedure at the 5\% FDR level to classify pixels as positive or not for defects.

\subsection{Computational Implementation}

The empirical null filter was implemented using \emph{ImageJ} \citep{abramoff2004image, perez2013image, schindelin2012fiji, schneider2012nih} by modifying the existing class \texttt{RankFilters}. It contains implementations of filters, such as the mean filter and median filter, using a circular kernel and multiple threads. Each thread filters a row in parallel.

@@

Contamination is the result of a linear transform of the test statistics $Z_{x,y}$. For example in this experiment, the image was multiplied by 2 and a gradient was added to it. Suppose the image does contain defects, then an example of a resulting distribution is
\begin{align}
  Z_{x,y}|H_{0,x,y}&\sim\normal(\mu_{0,x,y},2^2)
  \\
  Z_{x,y}|H_{1,x,y}&\sim\normal(2\mu_1+\mu_{0,x,y},2^2)
\end{align}
where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. This was used in this study to simulate a contaminated image with defects. The contaminated square defected image is shown in Fig.~\ref{fig:inference_defectSquare2Example}.

@@

It was suggested that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null \citep{efron2004large, schwartzman2008empirical}. In this simulated example, it is about $r>\SI{54}{\pixel}$. A kernel too small would treat the defects as null, making them difficult to detect.

The receiver operating characteristic (ROC) curve \citep{cook2007use, friedman2001elements, green1966signal, hanley1982meaning, metz1978basic} was studied in this experiment. The ROC is a parametric plot, plotting the true positive rate (sensitivity) against the false positive rate ($1-\text{specificity}$) for varying thresholds. The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}. Interpretations of the area do exist \citep{hanley1982meaning, metz1978basic} and discussed thoroughly \citep{cook2007use}.

@@

@@

The result from the simulation is shown Fig.~\ref{fig:inference_Experiment_DefectRadiusSquare}. The ROC area increased with kernel radius which highlighted that a filtered image with a good radius kernel can performance almost as well as though there was no contamination. It also appeared that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.

@@

In the experiment with the AM sample, the x-ray projection was manually segmented further as shown in Fig.~\ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the sample. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. The resulting inference is shown in Fig.~\ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}.

@@

@@

The main issue was how slow the filter was. Fig.~\ref{fig:inference_timing} shows the timings of the empirical null filter and the mean variance filter. For a filter to take more than a minute is unacceptable when used on the production line when typical filters can take a fraction of a second.

There are a few strategies to accelerate the filter. The empirical null filter may be accelerated using GPUs \citep{eklund2013medical, hwu2011gpu, yang2008parallel}, however efforts to implement the filter in \emph{CUDA} and \emph{C++} is fruitless if there may exist a faster method. Instead, accuracy may be sacrificed for speed by only estimating the null parameters for a number of regularly spaced pixels, the remaining pixels then do estimation through interpolation. The problem is that the assumption of a slow varying null parameter is required much more because of the use of interpolation, this may cause bigger problems due to the face to face transition observed in the experiments. It was found that if a bad solution was found for a point, then that solution would spread its bad solution to neighbour pixels due to the interpolation.

The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of each pixel in the kernel. Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline. On the other hand, there are methods which uses the histogram count and it was found that the estimation of the null parameters was insensitive to the histogram binning \citep{schwartzman2008empirical}.
